Comments on Latent Ranking

### 2020-09-14 output_scripts/aug_updates.Rmd
analysis for james

```{r compare fits from permuted and true data}
current_cohort <- 4

## load true model fit
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))

@@

mice_covars %>% ggplot(aes(true_rank,perm_rank)) + geom_point()

mice_covars %>% ggplot(aes(true_gam,perm_gam)) + geom_point()

mice_covars %>% ggplot(aes(true_zeta,perm_zeta)) + geom_point()

>>>>

```{r compare fits from permuted and true data}
current_cohort <- 1

for(current_cohort in 1:10){
  ## load true model fit
  load(paste(data_path,cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",cohort_names[current_cohort],
             ".RData",sep=''))

@@

  p <- mice_covars %>% ggplot(aes(true_rank,perm_rank)) + geom_point() +
    ggtitle(paste("Cohort ",current_cohort,sep = ""))

  q <- mice_covars %>% ggplot(aes(true_gam,perm_gam)) + geom_point()

  r <- mice_covars %>% ggplot(aes(true_zeta,perm_zeta)) + geom_point()

  grid.arrange(p,q,r, nrow = 1)
}

```
There does appear to be little to no structure in the estimated parameters 
after this permutation. For example, all `gamma` and `zeta` parameters display 
similar values, compared to the range seen in the original data. Similarly,
there is little to no correlation in the rankings 
obtained from the true events and the permuted events.
